Social Network Activation: \\The Application in Smartphone Use

### 2025-02-04 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
paper 2 slides

### Background

@@

### **Research Gap**

-   To address the consequences of lack of social engagement, prior studies primarily focus on social interaction volume. However, little attention is paid the the structure of one's social network.

-   Specifically, it is not clear whether activating different parts (e.g., core vs.periphery) of social network impact individuals differently.

### Context:

>>>>

### Motivation

@@

### **Gap**

-   To address the consequences of lack of social engagement, prior studies primarily focus on social interaction volume.

-   However, little attention is paid the the structure of one's social network. Specifically, it is not clear whether activating different parts (e.g., core vs.periphery) of social network impact individuals differently.

### Study/Methodology

-   We examine whether activating the core parts of social networks, as measured by K-Core, affects smartphone usage activities differently than activating peripheral parts.

##
### Study/Methodology
-   We leverage data sets collected from a series of longitudinal studies that tracked participants’ smartphone use, social networks, and physical activities. We measure social network activation in real-time and track its evolution for each participant, combining self-reported social network structure information and real-time mobile communications.
